abc

### 2024-08-18 randpython.qmd
newupd

```{pyodide-python}
#genpolycoeff(equn="alpha=k0 + k1*g + k2*h + k3*g**2 + k4*h**2 + k5*g*h + k6*h**3 + k7*g*h + k8*g**2*h + k9*g*h**2",solv="y")
#genpolycoeff(plr=1,parm=["alpha", "x", "y"], solv='y',grd=1,eur=[1, 4, 2])[0]
```

>>>>

```{pyodide-python}
#genpolycoeff(equn="alpha=k0 + k1*g + k2*h + k3*g**2 + k4*h**2 + k5*g*h + k6*h**3 + k7*g*h + k8*g**2*h + k9*g*h**2",solv="y")[0]
#genpolycoeff(plr=1,parm=["alpha", "x", "y"], solv='y',grd=1,eur=[1, 4, 2])[0]
```
